---
title: "Demo Content"
output: html_document
---

```{r setup, include=FALSE}
#options(repos = c(REPO_NAME = "https://colorado.posit.co/rspm/all/__linux__/bionic/2023-02-08+FmQYDCaW"))
#options(repos = c(REPO_NAME = "https://colorado.rstudio.com/rspm/all/__linux__/bionic/2022-09-29+Y3JhbiwxMDo1MzA5LDk6MTE1MDU5MDU7NjZFM0IyNA"))
options(repos = c(  INTERNAL = "https://colorado.posit.co/rspm/internal/__linux__/bionic/2022-09-30+T5_C-9yw",
                    INTERNAL_CRAN = "https://colorado.posit.co/rspm/all/__linux__/bionic/2023-02-08+FmQYDCaW",
                    CRAN = "https://cran.rstudio.com/"))

library(connectwidgets)
library(dplyr)
library(magrittr)
library(tidyverse)
library(shiny)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

client <- connect(
  server  = Sys.getenv("CONNECT_SERVER"),
  api_key = Sys.getenv("CONNECT_API_KEY")
  )

all_content <- client %>%
  content() %>%
  arrange(desc(updated_time))
```


## R

### Shiny App (CI/CD deployed)
```{r shiny}
all_content %>%
  filter(name == "learn_shinytest2") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/learn_shinytest2)

### Shiny App as Package

This Shiny app deployment has useful error messages in the logs 
```{r shiny2}
all_content %>%
  filter(name == "shinypackage") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/shinypackage)

### RMarkdown
```{r rrmarkdown}
all_content %>%
  filter(title == "rmd-penguins-report") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/r-examples/tree/main/rmd-penguins)

### RMarkdown with Blastula
```{r rrmarkdownblast}
all_content %>%
  filter(title == "rmd-blastula") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/r-examples/tree/main/rmd-blastula)

### Parameterized RMarkdown
```{r rrmarkdownparam}
all_content %>%
  filter(title == "Visualizing the Ocean Floor") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/code_sandbox/blob/main/R/rmarkdown_parameterized/Visualizing%20the%20Ocean%20Floor.Rmd)

### Plumber API
```{r plumber}
all_content %>%
  filter(title == "lisa_api_plumber") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/code_sandbox/tree/main/R/plumber)

### Pins 

```{r pins1}
all_content %>%
  #filter(title == "lisa_api_plumber") %>%
  filter(guid == "1d002e9f-1922-4fa7-bfbd-b3262dcde0ad" | title %in% c("Pin_mtcars", "Pin_mtcars_app") ) %>%
  #slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/code_sandbox/tree/main/R/pin)

### Pins

```{r pins2}
all_content %>%
  #filter(title == "lisa_api_plumber") %>%
  filter(guid == "1d002e9f-1922-4fa7-bfbd-b3262dcde0ad") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/code_sandbox/tree/main/R/pin)


### Pins: Scheduled

```{r pins3}
all_content %>%
  filter(title == "Pin_mtcars") %>%
  #filter(guid == "a84b4b78-537f-42a3-827c-7b377ee656d7") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/code_sandbox/tree/main/R/pin)

### Pins: in an App

```{r pins4}
all_content %>%
  filter(name == "pin_mtcars_app") %>%
  #filter(guid == "a84b4b78-537f-42a3-827c-7b377ee656d7") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/code_sandbox/tree/main/R/pin)


---

## Python

### Jupyter Notebook

```{r jupyter}
all_content %>%
  filter(title == "jupyter-notebook") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/leesahanders/code_sandbox/tree/main/Python/jupyter-notebook)

### Flask API

Model trained in spaCy via a Flask API
```{r flask}
all_content %>%
  filter(title == "Flask Sentiment Analysis API") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/flask-sentiment-analysis-api)


### Fast API

Fast API demo based on stock data
```{r fast}
all_content %>%
  filter(title == "Fast API Demo") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/fastapi-stock)


### Dash App

Dash Demo App
```{r dash}
all_content %>%
  filter(title == c("Demo_Temp_Dash")) %>%
  #filter(title %in% c("Demo_Temp_Dash", "dash-app") && owner_last_name %in% c("Anders", "Andre")) %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/dash-app)


### Streamlit App

Streamlit Demo showing income share
```{r streamlit}
all_content %>%
  filter(title == "streamlit-income-share") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/streamlit-income-share)

### Quarto with Python

Integration of Python into quarto projects with the jupyter kernel
```{r rmarkdownpython}
all_content %>%
  filter(title == "quarto-lightbox") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/quarto-lightbox)

---

## Bike Predict (R)

### Predict Shiny App
```{r bikepredict}
all_content %>%
  filter(title == "Bike Predict - App - Client App") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/jupyter-interactive-visualization)

### Web Data to Pins & Database
```{r webtopins}
all_content %>%
  filter(title == "Bike Predict - ETL Step 1 - Raw Data Refresh") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/bike_predict/blob/main/content/01-etl/01-raw-data-refresh/document.qmd)

### Train and Deploy Model (vetiver, pins, plumber, connect)
```{r deploy}
all_content %>%
  filter(title == "Bike Predict - Model Step 1 - Train and Deploy") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/bike_predict/blob/main/content/02-model/01-train-and-deploy-model/document.qmd)

### Model Monitoring and Accuracy (vetiver, pins, plumber, connect)
```{r metrics}
all_content %>%
  filter(title == "Bike Predict - Model Step 2 - Model Card" | title == "Bike Predict - Model Step 3 - Metrics") %>%
  #filter(title == "Bike Predict - Model Step 2 - Metrics") %>%
  #slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/bike_predict/blob/main/content/02-model/02-model-metrics/document.qmd)


---

## Other

### Example of what users see if they aren't granted access to the content 

```{r jupyter2}
all_content %>%
  filter(title == "Jupyter Interactive Visualization") %>%
  slice(1) %>%
  rsc_card()
```


[Source code](https://github.com/sol-eng/bike_predict/blob/main/content/02-model/02-model-metrics/document.qmd) to this connectwidget dashboard.


